### 2023-05-15 application.tex
sections

Another proof is possible for LCS since LCS are WSTS with a computable $\uparrow \post^*(S)$ \alain{à prouver et vérifier les autres hypothèses}
%
%%%
\subsection{LCM, VASS, semilinear VASS, Integer et Continuous VASS}

\begin{theorem}{}
Resilience is decidable for  lossy counter machines, semilinear VASS, Integer VASS when $\Safe$ and $\Bad$ are semilinear sets.
\end{theorem}

\begin{proof}
Resilience is decidable for lossy counter machines with $\Safe$ and $\Bad$ semilinear sets as a consequence of Theorem 3.6 in \cite{DBLP:conf/rp/Schnoebelen10} that implies that $\pred^*(\Safe)$ is a computable semilinear set. Hence since the inclusion between two semilinear sets is decidable, we deduce that  $\Bad \subseteq \pred^*(\Safe)$ is decidable.

%		semilinear VASS.
 \alain{le plus simple serait que $\pred^*(L)$ is semilinear because $\post^*(s)$ is semilinear , peut-être en inversant le VASS V en V'on aurait pred*(V)=post*(V') hence $post^*(L)$ is also semilinear ? hence pred ????}

%		Integer VASS
Recall that reachability is NP-complete for integer VASS. We consider semilinear sets in $\mathbb{Z}^d$.

\end{proof}

We also deduce immediately that resilience is decidable for $2$-VASS that have a semilinear reachability relation.

@@

open for VASS ???

%		\section{Control of a WSTS to be resilient}

>>>>

Another proof is possible for LCS since LCS are WSTS with a computable $\uparrow \post^*(S)$ \alain{à prouver et vérifier les autres hypothèses}
%
%%%
\subsection{VASS and variations of VASS}

\begin{theorem}{}
Resilience is decidable for VASS when $\Safe$ and $\Bad$ are semilinear sets.
\end{theorem}

\begin{proof}
\alain{faire d'abord la preuve pour les VASS.}
\end{proof}

\begin{theorem}{}
Resilience is decidable for lossy counter machines when $\Safe$ and $\Bad$ are semilinear sets.
\end{theorem}

\begin{proof}
Resilience is decidable for lossy counter machines with $\Safe$ and $\Bad$ semilinear sets as a consequence of Theorem 3.6 in \cite{DBLP:conf/rp/Schnoebelen10} that implies that $\pred^*(\Safe)$ is a computable semilinear set. Hence since the inclusion between two semilinear sets is decidable, we deduce that  $\Bad \subseteq \pred^*(\Safe)$ is decidable.
\end{proof}

\begin{theorem}{}
Resilience is decidable for integer VASS when $\Safe$ and $\Bad$ are semilinear sets.
\end{theorem}

\begin{proof}
		Recall that reachability is NP-complete for integer VASS. We consider semilinear sets in $\mathbb{Z}^d$.
\end{proof}

@@

### 2023-05-15 state-resilience.tex
sections

\begin{center}
\begin{tabular}{ | l | c | c | c | c |}
\hline  Hypothesis & strong %upward 
			compatibility ~ & $\uparrow post^*$ effective 
			& strong %upward 
					compatibility \textit{and} $\uparrow post^*$ effective \\ \hline
   SRP & Undecidable (Thm~\ref{srp up down}) & Decidable (Thm~\ref{post srp})  & Decidable (Thm~\ref{postcomputable})\\ \hline
   BSRP & Undecidable (Thm~\ref{srp up down}) &  ??  & Decidable (Thm~\ref{ref ozkan}) \\ \hline
      kSRP & Undecidable (Thm~\ref{srp up down}) & ?? & Decidable (Thm~\ref{ref ozkan}) \\ \hline
 \end{tabular}
\end{center}

>>>>

\begin{center}
\begin{tabular}{ | l | c | c | c | c |}
\hline  Hypothesis & strong %upward 
			compatibility ~ & $\uparrow post^*$ effective 
			& strong %upward 
					compatibility \textit{+} $\uparrow post^*$ effective \\ \hline
   SRP & Undecidable (Thm~\ref{srp up down}) & Decidable (Thm~\ref{post srp})  & Decidable (Thm~\ref{postcomputable})\\ \hline
   BSRP & Undecidable (Thm~\ref{srp up down}) &  ??  & Decidable (Thm~\ref{ref ozkan}) \\ \hline
      kSRP & Undecidable (Thm~\ref{srp up down}) & ?? & Decidable (Thm~\ref{ref ozkan}) \\ \hline
 \end{tabular}
\end{center}
